Transferability of clinical prediction models for early trauma care

### 2019-10-08 ManuscriptMarkdownAnon.Rmd
Add files via upload

---
title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Henriksson
- Dell D Saulnier
- Johanna Berg
- Martin Gerdin Wärnberg
date: "September 28, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

  *Background:* Trauma results in approximately four million deaths annually. Clinical
  prediction models are often used for triage in early trauma care. Previous research has
  indicated that transferring these models between different settings might adversely affect 
  model performance.

  *Methods:* Patients aged 15 years or older who were registered between 2011 and
  2016 in the Swedish national trauma registry, SweTrau, were included. Three sets
  of data were created: high- and low-volume centres, metropolitan and
  non-metropolitan centres, and multiple and single centres. Clinical
  prediction models were developed using logistic regression in each data set 
  and transferred within sets. Model performance was evaluated in all data
  sets using the mistriage rate, undertriage rate and overtriage rate. Multiple
  imputation using chained equations was used to handle missing data. Model
  performance was reported as medians with the 95% uncertainty interval across
  imputed data sets.

  *Results:* A total of `r total.number.of.patients ` patients were included. Model
  validation mistriage rate ranged from `r lowest.val.mistriage` 
  to `r highest.val.mistriage`, and the transferred model
  mistriage rate ranged from `r lowest.tran.mistriage` to `r highest.tran.mistriage`, 
  across all samples. The worst performance after transfer was the low-volume model transferred 
  to the high-volume sample, resulting in a significant mistriage rate increase of `r highest.comp.mistriage`, 
  primarily due to increased overtriage.

  *Conclusions:* In all samples, model transfer was associated with some degree of uncertainty. 
  Models developed in samples with high numbers of patients performed best after transfer, and the
  model developed in the low-volume sample performed worst after transfer.

>>>>

---
title: "Transferability of clinical prediction models for early trauma care"
date: "October 08, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

  *Background:* Trauma results in approximately four million deaths annually. Clinical
  prediction models are often used for triage in early trauma care. Transferring these 
  models between different settings might adversely affect model performance.

  *Methods:* Patients aged 15 years or older, registered between 2011-2016 
  in the Swedish national trauma registry, were included. Three data sets 
  were created: high- and low-volume centres, metropolitan and
  non-metropolitan centres, and multiple and single centres. Clinical
  prediction models were developed using logistic regression, and transferred within sets. 
  Model performance was evaluated in all data sets using the mistriage rate, undertriage 
  rate and overtriage rate. Model performance was reported as medians with the 95% uncertainty 
  interval across imputed data sets.

  *Results:* `r total.number.of.patients ` patients were included. Transferred model
  mistriage rate ranged from `r lowest.tran.mistriage` to `r highest.tran.mistriage`, 
  across all samples. The worst performance after transfer was the low-volume model 
  transferred to the high-volume sample, resulting in a significant mistriage rate 
  increase of `r highest.comp.mistriage`.

  *Conclusions:* In all samples, model transfer was associated with some uncertainty. 
  Models developed in samples with high numbers of patients generally performed best after 
  transfer, and the model developed in the low-volume sample performed worst after transfer.
